Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-30 demystify.tex
updates

\begin{mybox}
The latest version of this document is available at

@@

Students understandably get excited about their upcoming PhD journey and want to buy new computer equipment and electronics to prepare. However, you should check with your prof. first.  They might have funding to buy you computers and other equipment (e.g., software, books, keyboards, headphones, tablets, etc). Many CS programs also provide budget or computer equipment to incoming PhD students (e.g., a laptop).

@@

\chapter{Visa and all that for International Students}\label{sec:visa}

@@

\item \textbf{Curricular Practical Training (CPT):} This program allows you to participate in internships or practical training that is an integral part of their academic curriculum. CPT must be related to the student's field of study and can be full-time or part-time. It requires prior authorization from the Designated School Official (DSO) and must be completed before graduation.

\item \textbf{Optional Practical Training (OPT):} OPT provides up to 12 months of work authorization for students before or after completing their degree. For students in STEM fields, there is an additional 24-month extension available. OPT requires prior application and approval from the United States Citizenship and Immigration Services (USCIS).

>>>>

\begin{mybox}
This document will be updated regularly to reflect the latest information and updates in the admission process. Its latest version is available at

@@

Students understandably get excited about their upcoming PhD journey and want to buy new computer equipment and electronics to prepare. However, you should first check with your professor.  They might have funding to buy you computers and other equipment (e.g., software, books, keyboards, headphones, tablets, etc). Many CS programs also provide budget or computer equipment to incoming PhD students (e.g., a laptop).

@@

\chapter{Visa for International Students}\label{sec:visa}

@@

\item \textbf{Curricular Practical Training (CPT):} CPT allows you to participate in internships or practical training that is an integral part of their academic curriculum. CPT must be related to your field of study and can be full-time or part-time. It requires prior authorization from your university and must be completed before graduation.

\item \textbf{Optional Practical Training (OPT):} OPT provides up to 12 months of work authorization for students before or after completing their degree. For students in STEM fields, there is an additional 24-month extension available. OPT requires prior application and approval from USCIS.
